How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-30 tse-paper/content.tex
Add publication year figure

% turned into an itemize again cause the 'sentence' around it was
% rather broken and item-ish anyways
To fill this gap, we adapted and implemented three novel, prototypical
implementations to
automatically analyze build logs (step 2).
The ideas behind the implementations are based on promising approaches
adopted from other research fields and existing build log analysis
techniques.
In this article, we present three techniques that analyze a build log
by retrieving a substring (chunk) that describes a
specific information:
\begin{itemize}
	\item \emph{Program Synthesis by Example (PBE)}, a technique
	able to
	automatically synthesize regular expressions,
	\item a technique based on information
	retrieval, using \emph{Common Text Similarity (CTS)}
	\item inspired by the manual ad hoc search for key parts in the
	log, a
	technique employing \emph{Keyword Search (KWS)}
\end{itemize}
% a technique 1) able to automatically synthesize regular expressions,
% called \emph{Program Synthesis by Example (PBE)}, a technique
% 2) based on information
% retrieval, using \emph{Common Text Similarity (CTS)}	and 3)
% inspired by the manual ad hoc search for key parts in the log, a
% technique employing \emph{Keyword Search (KWS)}.
These three approaches---synthesized regular expressions,
text similarity, and
keyword search---have
different strengths and weaknesses.
As a consequence,
in the second research question we ask:

@@

In this section, we give a general overview over our paper population.
We then present the results of the analysis phase, along the
RQs 1.1 through 1.3.

\subsubsection{Descriptive Study Statistics}
To be done.
% TODO moritz: age of papers (graph), kind of
% publication (master, paper)
% published (y, n)

>>>>

% turned into an itemize again cause the 'sentence' around it was
% rather broken and item-ish anyways
To fill this gap, we adapted and implemented three novel, prototypical
implementations to
automatically analyze build logs (step 2).
The ideas behind the implementations are based on promising approaches
adopted from other research fields and existing build log analysis
techniques.
In this article, we present three techniques that analyze a build log
by retrieving a substring (chunk):
\begin{itemize}
	\item \emph{Program Synthesis by Example (PBE)}, a technique
	able to
	automatically synthesize regular expressions,
	\item a technique based on information
	retrieval, using \emph{Common Text Similarity (CTS)}
	\item inspired by the manual ad hoc search for key parts in the
	log, a
	technique employing \emph{Keyword Search (KWS)}
\end{itemize}
% a technique 1) able to automatically synthesize regular expressions,
% called \emph{Program Synthesis by Example (PBE)}, a technique
% 2) based on information
% retrieval, using \emph{Common Text Similarity (CTS)}	and 3)
% inspired by the manual ad hoc search for key parts in the log, a
% technique employing \emph{Keyword Search (KWS)}.
These three approaches---synthesized regular expressions,
text similarity, and
keyword search---have
different strengths and weaknesses.
As a consequence,
in the second research question we ask:

@@

In this section, we give a general overview over our paper population.
We then present the results of the analysis phase along RQs 1.1 through 1.3.

\subsubsection{Descriptive Study Statistics}
To be done.

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/years.pdf}
		\caption{Number of works analyzing build logs per year.}
		\label{fig:failure-reason-PBE}
\end{figure}

% TODO moritz: age of papers (graph), kind of
% publication (master, paper)
% published (y, n)
